The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes

### 2022-09-09 report/accepted-manuscript.Rmd
final version

---
output: 
  stevetemplates::article:
    fig_caption: true
bibliography: references.bib
urlcolor: black
linkcolor: black
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage[para,online,flushleft]{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
   - \usepackage{hyperref}
   - \usepackage{array}   
   - \usepackage{caption}
   - \usepackage{graphicx}
   - \usepackage{epstopdf}
   - \usepackage{siunitx}
   - \usepackage{multirow}
   - \usepackage{hhline}
   - \usepackage{calc}
   - \usepackage{tabularx}
   - \usepackage{fontawesome}
   - \usepackage{amsthm}
   - \newtheorem{hypo}{Hypothesis}
biblio-style: apsr
title: "The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
author:
  - name: Maurits Meijers
  - affiliation: Radboud University Nijmegen
  - name: Mariken A.C.G. van der Velden
  - affiliation: Vrije Universiteit Amsterdam
thanks: "Replication files are available on the author's Github account (https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes). **Current version**: `r format(Sys.time(), '%B %d, %Y')`;"
anonymous: FALSE
abstract: "Populists believe in the sovereignty of the people. Yet, the people can be construed in ethnic terms or in civic terms. Using a novel wording experiment in Germany (N=7,034), we examine whether ethnic or civic conceptions of 'the people' affect respondents' adherence agreement to key populist attitude items. '_Volk_' in German has an ethno-nationalist connotation and has been used throughout history to signify 'ethnic Germans'. The concept '_Bürger_', or citizens, by contrast, lacks an ethnic undercurrent. Similar ethnic connotations of 'the people' are also common in other languages. We find that there are statistically significant differences between items framed in an ethnic and a civic manner -- and that this differs per item. This relationship is significantly moderated by respondents' degree of exclusive national identity and voting behaviour for the radical right. Our findings suggest that the way in which the people is conceptualized has important implications for the measurement of populist attitudes. When populist attitudes are measured with an ethnic understanding of the 'the people', the construct is biased toward right-wing populism, inhibiting the measurement of populism as a `thin-ideology'. Moreover, we demonstrate the importance of careful translations in comparative research, since some translated synonyms carry different meanings, and thereby change the concept under investigation."

>>>>

---
output: 
  stevetemplates::article:
    fig_caption: true
bibliography: references.bib
urlcolor: black
linkcolor: black
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage[para,online,flushleft]{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
   - \usepackage{hyperref}
   - \usepackage{array}   
   - \usepackage{caption}
   - \usepackage{graphicx}
   - \usepackage{epstopdf}
   - \usepackage{siunitx}
   - \usepackage{multirow}
   - \usepackage{hhline}
   - \usepackage{calc}
   - \usepackage{tabularx}
   - \usepackage{fontawesome}
   - \usepackage{amsthm}
   - \newtheorem{hypo}{Hypothesis}
biblio-style: apsr
title: "The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
author:
  - name: Maurits Meijers
  - affiliation: Radboud University Nijmegen
  - name: Mariken A.C.G. van der Velden
  - affiliation: Vrije Universiteit Amsterdam
thanks: "Replication files are available on the author's Github account (https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes); Authorship order is alphabetical due to equal contribution. _Current version accepted at European Journal of Political Research_"
anonymous: FALSE
abstract: "Populists believe in the sovereignty of the people. Yet, the people can be construed in ethnic terms or in civic terms. Using a novel wording experiment in Germany (N=7,034), we examine whether ethnic or civic conceptions of 'the people' affect respondents' adherence agreement to key populist attitude items. '_Volk_' in German has an ethno-nationalist connotation and has been used throughout history to signify 'ethnic Germans'. The concept '_Bürger_', or citizens, by contrast, lacks an ethnic undercurrent. Similar ethnic connotations of 'the people' are also common in other languages. We find that there are statistically significant differences between items framed in an ethnic and a civic manner -- and that this differs per item. This relationship is significantly moderated by respondents' degree of exclusive national identity and voting behaviour for the radical right. Our findings suggest that the way in which the people is conceptualized has important implications for the measurement of populist attitudes. When populist attitudes are measured with an ethnic understanding of the 'the people', the construct is biased toward right-wing populism, inhibiting the measurement of populism as a `thin-ideology'. Moreover, we demonstrate the importance of careful translations in comparative research, since some translated synonyms carry different meanings, and thereby change the concept under investigation."
